---
title: "Causal Claims Tables"
output: pdf_document
---

```{r setup, include=FALSE,message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
flextable::set_flextable_defaults(
  fonts_ignore = TRUE
  )
targets::tar_read(results_consc_depression)
targets::tar_read(results_consc_depression_income)
targets::tar_read(results_neuroticism)
targets::tar_read(results_neuroticism_income)
targets::tar_read(results_phys_consc)
targets::tar_read(summary_stats_table)

targets::tar_read(results_linear_regression_phys_consc)
targets::tar_read(results_linear_regression_neuroticism_income)
targets::tar_read(results_linear_regression_neuroticism)
targets::tar_read(results_linear_regression_consc_depression)
targets::tar_read(results_linear_regression_consc_depression_income)
```

# Summary Statistics

```{r, message = FALSE}
summary_stats_table
```


# Illustration 1:  Does conscientiousness causally influence physical health?

## OLS: Does Conscientiousness Causally Influence Physical Health (At Age 50)?

```{r, message = FALSE}
results_linear_regression_phys_consc
```
## Discordant: Does Conscientiousness Causally Influence Physical Health (At Age 50)?

```{r, message = FALSE}
results_phys_consc
```

# Illustration 2:  Does conscientiousness causally influence mental health?


## OLS: Does Conscientiousness Causally Influence Mental Health (Depression)?

```{r, message = FALSE}
results_linear_regression_consc_depression
```

## OLS: Does Conscientiousness Causally Influence Mental Health (Depression) with Income and Highest Grade Level (At Age 50) as Covariates?

```{r, message = FALSE}
results_linear_regression_consc_depression_income
```

## Discordant: Does Conscientiousness Causally Influence Mental Health (Depression)?

```{r, message = FALSE}
results_consc_depression
```

## Discordant: Does Conscientiousness Causally Influence Mental Health (Depression) with Income and Highest Grade Level (At Age 50) as Covariates?

```{r, message = FALSE}
results_consc_depression_income
```


# Illustration 3 Does neuroticism causally influence mental health?

## OLS: Does Neuroticism Causally Influence Mental Health (Depression)?

```{r, message = FALSE}
results_linear_regression_neuroticism
```

## OLS: Does Neuroticism Causally Influence Mental Health (Depression) with Income and Highest Grade Level (At Age 50) as Covariates?

```{r, message = FALSE}
results_linear_regression_neuroticism_income
```


## Discordant: Does Neuroticism Causally Influence Mental Health (Depression)?

```{r, message = FALSE}
results_neuroticism
```

## Discordant: Does Neuroticism Causally Influence Mental Health (Depression) with Income and Highest Grade Level (At Age 50) as Covariates?

```{r, message = FALSE}
results_neuroticism_income
```
